### 2016-06-07 tasks_and_ideas.tex
cheers
added task: definiing unlinkability as a security notion

\begin{itemize}
\item Prove that a Bloom filter using hash functions defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$, for secret keys $K0,K1$, is FP-secure when either~$f$ or~$g$ is a secure PRF.  (This is a real proposal, see the intro.)  Interesting that these $h_j$ are not independent, even if $f_{K0},g_{K1}$ are replaced by independent random functions, whereas the traditional BF false positive analysis treats the $h_j$ as independent.  I wonder if the analysis for determining the number of hash functions still holds when the $h_j$ are dependent?  Note: definitely not in general, just consider $h_j$ a fixed function for all $j$; but it's an interesting question to ask for this particular kind of dependence.  (Should check the Kirsh, Mitzenmacher paper first; they probably address this. \tsnote{They show that two random functions, combined in this way (for a prime~$m$), suffices.  No increase in asymptotic FP probability.  They also argue that construction of $h_j$ is thus better than one can do using generic pairwise-independent $h_j$.  They also point out the difference between the FP \emph{probability} (the probability that a particular $x \not\in S$ causes a FP) and the FP \emph{rate} (the average FP probability over $x \not\in S$), which I hadn't really considered before. })

@@

\item  If I recall properly, a Bloom filter leaks the number of elements that it represents, if you know the filter size and the number of hash functions.  Verify this.  Also, what about set-intersection attacks on Bloom filters?

\item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.

@@

\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.

@@

\item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?  Are Bloom filters used in edge network servers for big providers like Facebook, LinkedIn, Google, etc.?

\item Generally speaking, can we characterize operational settings in a way that surfaces an interesting security/performance trade-off?  For example, the Bloom filters used by Akamai's CDN are on the order of 600-700MB in size and are shared among several machines in a local area.  The Bloom filters used in a simple spam-detection system (do these exist) are likely to be much smaller, maintained locally on a single machine, and much easier to update.  Solutions in one setting are not going to be useful in another....

>>>>

\heading{Theory tasks.}
\begin{itemize}
\item Prove that a Bloom filter using hash functions defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$, for secret keys $K0,K1$, is FP-secure when either~$f$ or~$g$ is a secure PRF.  (This is a real proposal, see the intro.)  Interesting that these $h_j$ are not independent, even if $f_{K0},g_{K1}$ are replaced by independent random functions, whereas the traditional BF false positive analysis treats the $h_j$ as independent.  I wonder if the analysis for determining the number of hash functions still holds when the $h_j$ are dependent?  Note: definitely not in general, just consider $h_j$ a fixed function for all $j$; but it's an interesting question to ask for this particular kind of dependence.  (Should check the Kirsh, Mitzenmacher paper first; they probably address this. \tsnote{They show that two random functions, combined in this way (for a prime~$m$), suffices.  No increase in asymptotic FP probability.  They also argue that construction of $h_j$ is thus better than one can do using generic pairwise-independent $h_j$.  They also point out the difference between the FP \emph{probability} (the probability that a particular $x \not\in S$ causes a FP) and the FP \emph{rate} (the average FP probability over $x \not\in S$), which I hadn't really considered before. })

@@

\item  If I recall properly, a Bloom filter leaks the number of elements that it represents, if you know the filter size and the number of hash functions.  Verify this.  \tsnote{Approximately true.  If the distribution of the expected number of zero bits is tight around its mean, then you can use the actual number of 0-bits as the expected number, and then deduce the size of the set.}  Also, what about set-intersection attacks on Bloom filters?
\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.

\item Formalize ``unlinkability'', i.e. given some initial information about two representations $M_0,M_1$ before an element~$x$ is added, an adversary can't distinguish between $M_0 \cup x$ and $M_1 \cup x$ (abusing notation).  \tsnote{This is somewhat defined in Kerschbaum.}

\item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?  Are Bloom filters used in edge network servers for big providers like Facebook, LinkedIn, Google, etc.?
\end{itemize}

\heading{Systems-y tasks.}
\begin{itemize}
\item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.

@@

@@

\item Generally speaking, can we characterize operational settings in a way that surfaces an interesting security/performance trade-off?  For example, the Bloom filters used by Akamai's CDN are on the order of 600-700MB in size and are shared among several machines in a local area.  The Bloom filters used in a simple spam-detection system (do these exist) are likely to be much smaller, maintained locally on a single machine, and much easier to update.  Solutions in one setting are not going to be useful in another.  Likewise, attacks in one setting may not scale to another, e.g. the preimage-finding/polluting-point attacks in that INRIA whitepaper.
